Understanding domestic abuse

### 2019-07-23 pathways_to_impact.tex

See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.

@@

At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015. (https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf) We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

@@

2
a determining factor for officer or staff recruitment. To this end, we will complement the
behavioural science evidence base with a survey of the public to measure the properties of
officers they desire (with Chief Constable Sue Fish, Nottinghamshire; Assistant
Commissioner Martin Hewitt, MPS; and the (London) Mayor’s Office for Police And Crime).
We will use a market research company to measure, from a representative sample of the UK
population, their views on the age, sex, race, ethnicity, religious affiliation, psychological
traits. Our objective is to start and develop a public dialogue.
Management. What is the impact of performance development review gradings on both
individual behaviours and those of their subordinates (Deputy Commissioner Craig Mackey
and Chief Superintendent Robert Jones). That is, what outcomes in are associated with
better line managers? We have already found that the highest scoring line managers have
subordinates with a 20% reduction in the incidence of sickness. We have also identified
significant variability across the Met within the sickness and complaints measures, with
some boroughs having half the rates of sickness and complaints of others, and some
boroughs having large changes within the 5-year period of the data. The mechanism for
impact within the MPS is the HR change programmes (Robin Wilkinson, HR Director).
Absenteeism and complaints. Using the data we already have, we see a very strong
association between sickness and complaints. Among officers who have no complaint in the
5-year period, 63% of officers have one or more episode of sickness. But among officers
who have a complaint, 84% have one of more sickness. Further, econometric panel data
analysis shows that there is almost no association between previous complaints and current
sickness or vice versa: Complaints do not appear to cause sickness, and sickness does not
put officers at greater risk of a complaint. The logical conclusion from this work is that there
are strong individual difference predictors of these measures—and we have
conscientiousness and agreeableness from the online lab as prime candidates. So key
questions are why are complaints and sickness associated (Chief Constable Sue Fish,
Nottinghamshire)? Which individual differences predict complaints and sickness (Chief
Superintendent Robert Jones)?
Right for the role? Do certain types of behavioural attributes (personality, risk attitudes)
coalesce in specific police functions, such as specialist operations or investigations (Chief
Officer Mike Bowron, States of Jersey Police)?
Bad cops or bad circumstances? Are there career hotspots for misconduct or serious
substantiated complaints (Deputy Commissioner Craig Mackey). Can we provide early
intervention warnings for officers at greatest risk of misconduct? The mechanism for impact
is through Professional Standards (Deputy Assistant Commissioner Fiona Taylor), to help
design career paths that avoid potentially potent placements or role succession that
materially increase the risk of misconduct.
We will also offer a series of four 1-day Behaviour Masterclasses to Senior Officers'
departments in the final year of the project. Classes will be advertised via the College of
Policing, the National Police Chief’s Council, and Warwick’s Centre for Operational Policing
Research. We will target the chief officers responsible for policy and implementation within
their force, and members of their teams. Classes will be co-led by Stewart or Ritchie, and an
officer. We will use feedback to shape the further development of the research.

>>>>

\documentclass[11pt, a4paper]{article}

% Helvetica
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

% 2cm margins
\usepackage[margin=2cm]{geometry}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[center]{caption}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage{threeparttable}
%\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}

\usepackage{apacite} 
%\usepackage{setspace}
%\doublespacing

\definecolor{green}{rgb}{0,1,0}
\newcommand{\NS}[1] {{\textcolor{green}{#1}}}
\newcommand{\TM}[1] {{\textcolor{orange}{#1}}}
\newcommand{\AT}[1] {{\textcolor{blue}{#1}}}

\begin{document}
\title{Understanding domestic abuse}
\date{}
\maketitle

%See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.

@@

At the College of Policing (situated just a few miles from Warwick campus) we will work within the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{framework of the Authorised Professional Practice on domestic abuse}, released in 2015.  
We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

@@

2
a determining factor for officer or staff recruitment. To this end, we will complement the
behavioural science evidence base with a survey of the public to measure the properties of
officers they desire (with Chief Constable Sue Fish, Nottinghamshire; Assistant
Commissioner Martin Hewitt, MPS; and the (London) Mayor’s Office for Police And Crime).
We will use a market research company to measure, from a representative sample of the UK
population, their views on the age, sex, race, ethnicity, religious affiliation, psychological
traits. Our objective is to start and develop a public dialogue.
Management. What is the impact of performance development review gradings on both
individual behaviours and those of their subordinates (Deputy Commissioner Craig Mackey
and Chief Superintendent Robert Jones). That is, what outcomes in are associated with
better line managers? We have already found that the highest scoring line managers have
subordinates with a 20% reduction in the incidence of sickness. We have also identified
significant variability across the Met within the sickness and complaints measures, with
some boroughs having half the rates of sickness and complaints of others, and some
boroughs having large changes within the 5-year period of the data. The mechanism for
impact within the MPS is the HR change programmes (Robin Wilkinson, HR Director).
Absenteeism and complaints. Using the data we already have, we see a very strong
association between sickness and complaints. Among officers who have no complaint in the
5-year period, 63% of officers have one or more episode of sickness. But among officers
who have a complaint, 84% have one of more sickness. Further, econometric panel data
analysis shows that there is almost no association between previous complaints and current
sickness or vice versa: Complaints do not appear to cause sickness, and sickness does not
put officers at greater risk of a complaint. The logical conclusion from this work is that there
are strong individual difference predictors of these measures—and we have
conscientiousness and agreeableness from the online lab as prime candidates. So key
questions are why are complaints and sickness associated (Chief Constable Sue Fish,
Nottinghamshire)? Which individual differences predict complaints and sickness (Chief
Superintendent Robert Jones)?
Right for the role? Do certain types of behavioural attributes (personality, risk attitudes)
coalesce in specific police functions, such as specialist operations or investigations (Chief
Officer Mike Bowron, States of Jersey Police)?
Bad cops or bad circumstances? Are there career hotspots for misconduct or serious
substantiated complaints (Deputy Commissioner Craig Mackey). Can we provide early
intervention warnings for officers at greatest risk of misconduct? The mechanism for impact
is through Professional Standards (Deputy Assistant Commissioner Fiona Taylor), to help
design career paths that avoid potentially potent placements or role succession that
materially increase the risk of misconduct.
We will also offer a series of four 1-day Behaviour Masterclasses to Senior Officers'
departments in the final year of the project. Classes will be advertised via the College of
Policing, the National Police Chief’s Council, and Warwick’s Centre for Operational Policing
Research. We will target the chief officers responsible for policy and implementation within
their force, and members of their teams. Classes will be co-led by Stewart or Ritchie, and an
officer. We will use feedback to shape the further development of the research.
\newpage

\bibliographystyle{apacite}
\bibliography{domesticabuse_refs}

\end{document}
